---
title: "Results"
author: "Fonti Kar"
date: "`r Sys.Date()`"
output:
  word_document:
    reference_docx: Style_guide.docx
  html_document:
    df_print: paged
---

```{r setup, eval = TRUE, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(eval = FALSE,
                      echo = FALSE, 
                      include = FALSE, 
                      warning = FALSE,
                      message = FALSE)
rm(list=ls())
sessionInfo()

# R version 3.6.1 (2019-07-05)
# Platform: x86_64-apple-darwin15.6.0 (64-bit)
# Running under: macOS High Sierra 10.13.6

pacman::p_load(dplyr, magrittr, ggplot2, purrr, Rphylopars, phytools, GGally, mice, janitor, patchwork, GGally, psych, brms, mi, pander,latex2exp, stringr)

my_theme <- theme(#legend.position = "none",
  legend.position = "bottom",
  legend.text =element_text(size = 14),
  legend.title =element_text(size = 14, face = "bold"),
  panel.grid.major = element_blank(), 
  panel.grid.minor = element_blank(),
  axis.text=element_text(size=16),
  axis.title=element_text(size=16),
  plot.title = element_text(size = 20, face = "bold", hjust = 0.5),
  plot.background = element_rect(colour = "white"))

source("R/functions/helper.R")
```

```{r}
## Read in data
data <-read.csv("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/data/processed/Long_Tinc_MR.csv", stringsAsFactors = F)
mi_data <-read.csv("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/data/processed/Long_Tinc_MR_MI.csv", stringsAsFactors = F)

str(data)

## We don't need prior_temp
data %<>% select(-prior_temp)
```

## Model selection of random effects structure
We fitted four different models with different combination of random effects to determine what is the best model structure for data analysis.
Based on previous study presented in Chapter X (Kar et al 2020), we found that individuals displayed consistent variation in their response to acute temperature change. We also found that within individual variation as well as measurement error varied across temperatures. We therefore included random linear slope for individual identity and the measurement error term. In some models, we also assumed individual variation and measurement error were constant by included only a random intercept for these terms. In one model, we allowed residuals which includes within individual variation to vary with temperature. 

```{r, eval = FALSE, cache = TRUE}
## Tabulatng it nicely
#Read in models
mod.2.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/mod.2.obj") #Homo resids linear slopes for all
mod.4.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/mod.4.obj") #Intercept ME and series
# mod.4.mm.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/mod.4.mm.obj") 
mod.5.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/mod.5.obj") #Intercept ID, slopes for ME and SampSessions
mod.6.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/mod.6.obj") #Intercept for ID, ME and slope for session

#Compute their IC
waic_mod.2.obj <- waic(mod.2.obj)
loo_mod.2.obj <- loo(mod.2.obj)

# waic_mod.3.obj <- waic(mod.3.obj)
# loo_mod.3.obj <- loo(mod.3.obj)

waic_mod.4.obj <- waic(mod.4.obj)
loo_mod.4.obj <- loo(mod.4.obj)
# loo_mod.4.mm.obj <- loo(mod.4.mm.obj, moment_match = T)
# loo_mod.4.obj_mm <- loo_moment_match(x = mod.4.mm.obj, loo = loo_mod.4.mm.obj) #Submitted amd gonna test it out...nope

waic_mod.5.obj <- waic(mod.5.obj)
loo_mod.5.obj <- loo(mod.5.obj)

waic_mod.6.obj <- waic(mod.6.obj)
loo_mod.6.obj <- loo(mod.6.obj)

#Creating table
RE_compare_WAIC <- data.frame(matrix(nrow = 4, ncol = 4))
colnames(RE_compare_WAIC) <- c("Model", "WAIC value", "ELPD Diff", "SE Diff")

#Fill in Model str
RE_compare_WAIC[1,1] <- c("(1 + temp | id) + (1 + temp | series_temp)") #mod.2.obj
RE_compare_WAIC[2,1] <- c("(1 | id) + (1 + temp | series_temp)") #mod.5.obj
RE_compare_WAIC[3,1] <- c("(1 + temp | id) + (1 | series_temp)") #mod.4.obj
RE_compare_WAIC[4,1] <- c("(1 + temp + temp_I2 | id) + (1 + temp + temp_I2 | series_temp)") #mod.6.obj
#RE_compare_WAIC[5,1] <- c("(1 + temp | id) + (1 + temp | series_temp), sigma ~ temp") #mod.3.obj

#Fill in WAIC estimate
RE_compare_WAIC[1,2] <-  waic_mod.2.obj$estimates[3,1] %>% round(2) #mod.2.obj
RE_compare_WAIC[2,2] <-  waic_mod.5.obj$estimates[3,1] %>% round(2) #mod.5.obj
RE_compare_WAIC[3,2] <-  waic_mod.4.obj$estimates[3,1] %>% round(2) #mod.4.obj
RE_compare_WAIC[4,2] <-  waic_mod.6.obj$estimates[3,1] %>% round(2) #mod.6.obj
#RE_compare_WAIC[5,2] <-  waic_mod.3.obj$estimates[3,1] %>% round(2) #mod.3.obj

#Fill in ELPD of diff estimate
WAIC_compare <- loo_compare(waic_mod.4.obj, waic_mod.5.obj, waic_mod.2.obj, waic_mod.6.obj)

#Rerrange by WAIC values
RE_compare_WAIC %<>% arrange(`WAIC value`)

RE_compare_WAIC[1,3] <-  WAIC_compare[1,1] %>% round(2) 
RE_compare_WAIC[2,3] <-  WAIC_compare[2,1] %>% round(2) 
RE_compare_WAIC[3,3] <-  WAIC_compare[3,1] %>% round(2) 
RE_compare_WAIC[4,3] <-  WAIC_compare[4,1] %>% round(2) 
#RE_compare_WAIC[5,3] <-  WAIC_compare[5,1] %>% round(2) 
  
#Fill in SE of diff estimate
RE_compare_WAIC[1,4] <-  WAIC_compare[1,2] %>% round(2) 
RE_compare_WAIC[2,4] <-  WAIC_compare[2,2] %>% round(2) 
RE_compare_WAIC[3,4] <-  WAIC_compare[3,2] %>% round(2) 
RE_compare_WAIC[4,4] <-  WAIC_compare[4,2] %>% round(2) 
#RE_compare_WAIC[5,4] <-  WAIC_compare[5,2] %>% round(2) 

#Tabulating LOO values
RE_compare_LOO <- data.frame(matrix(nrow = 4, ncol = 4))
colnames(RE_compare_LOO) <- c("Model", "LOO value", "ELPD Diff", "SE Diff")

#Fill in Model str
RE_compare_LOO[1,1] <- c("(1 | id) + (1 + temp | series_temp)") #mod.5.obj
RE_compare_LOO[2,1] <- c("(1 + temp | id) + (1 + temp | series_temp)") #mod.2.obj 
RE_compare_LOO[3,1] <- c("(1 + temp | id) + (1 | series_temp)") #mod.4.obj
RE_compare_LOO[4,1] <- c("(1 + temp + temp_I2 | id) + (1 + temp + temp_I2 | series_temp)") #mod.6.obj
#RE_compare_LOO[5,1] <- c("(1 + temp | id) + (1 + temp | series_temp), sigma ~ temp") #mod.3.obj

#Fill in LOO estimate
RE_compare_LOO[1,2] <-  loo_mod.5.obj$estimates[3,1] %>% round(2) #mod.5.obj
RE_compare_LOO[2,2] <-  loo_mod.2.obj$estimates[3,1] %>% round(2) #mod.2.obj
RE_compare_LOO[3,2] <-  loo_mod.4.obj$estimates[3,1] %>% round(2) #mod.4.obj
RE_compare_LOO[4,2] <-  loo_mod.6.obj$estimates[3,1] %>% round(2) #mod.6.obj
#RE_compare_LOO[5,2] <-  loo_mod.3.obj$estimates[3,1] %>% round(2) #mod.3.obj

#Fill in ELPD of diff estimate
LOO_compare <- loo_compare(loo_mod.4.obj, loo_mod.5.obj, loo_mod.2.obj, loo_mod.6.obj)

#Rerrange by WAIC values
RE_compare_LOO %<>% arrange(`LOO value`)

RE_compare_LOO[1,3] <-  LOO_compare[1,1] %>% round(2) #mod.3.obj
RE_compare_LOO[2,3] <-  LOO_compare[2,1] %>% round(2) #mod.5.obj
RE_compare_LOO[3,3] <-  LOO_compare[3,1] %>% round(2) #mod.4.obj
RE_compare_LOO[4,3] <-  LOO_compare[4,1] %>% round(2) #mod.2.obj
#RE_compare_LOO[5,3] <-  LOO_compare[5,1] %>% round(2) #mod.6.obj
  
#Fill in SE of diff estimate
RE_compare_LOO[1,4] <-  LOO_compare[1,2] %>% round(2) #mod.3.obj
RE_compare_LOO[2,4] <-  LOO_compare[2,2] %>% round(2) #mod.5.obj
RE_compare_LOO[3,4] <-  LOO_compare[3,2] %>% round(2) #mod.4.obj
RE_compare_LOO[4,4] <-  LOO_compare[4,2] %>% round(2) #mod.2.obj
#RE_compare_LOO[5,4] <-  LOO_compare[5,2] %>% round(2) #mod.6.obj
```

```{r, eval = FALSE, include = TRUE}
pander(RE_compare_WAIC,
       justify = "lccc",
       #split.cell = 80,
       caption = "Table SX Comparisons of WAIC values for four models with different combinations of random effects structures for individual variance and measurement error")

pander(RE_compare_LOO,
       justify = "lccc",
       #split.cell = 80,
       caption = "Table SX Comparisons of LOO values for four models with different combinations of random effects structures for individual variance and measurement error")
```

## Heterogenous variance 
```{r}
mod.4.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/mod.4.obj") #Intercept ME HOMO
mod.4.het.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/mod.4.het.obj") #Intercept ME Hetero

#Add IC
waic_mod.4.obj<- waic(mod.4.obj)
loo_mod.4.obj <- loo(mod.4.obj)

waic_mod.4.het.obj <- waic(mod.4.het.obj)
loo_mod.4.het.obj <- loo(mod.4.het.obj)

#Compare
WAIC_compare_resid <- loo_compare(waic_mod.4.obj, waic_mod.4.het.obj)
LOO_compare_resid  <- loo_compare(loo_mod.4.obj, waic_mod.4.het.obj)

#Creating table
Resid_compare_WAIC <- data.frame(matrix(nrow = 4, ncol = 5))
colnames(Resid_compare_WAIC) <- c("Model", "IC type",  "IC value", "ELPD Diff", "SE Diff")
Resid_compare_WAIC$Model <- rep(c("Homogenous residuals", "Heterogennous residuals"), 2)
Resid_compare_WAIC$`IC type` <- rep(c("WAIC", "LOO"), each = 2)

#WAIC
Resid_compare_WAIC[1,3] <- waic_mod.4.obj$estimates[3,1] %>% round(2)
Resid_compare_WAIC[2,3] <- waic_mod.4.het.obj$estimates[3,1] %>% round(2)

#LOO
Resid_compare_WAIC[3,3] <- loo_mod.4.obj$estimates[3,1] %>% round(2)
Resid_compare_WAIC[4,3] <- loo_mod.4.het.obj$estimates[3,1] %>% round(2)

#ELPD and SE
#WAIC
Resid_compare_WAIC[1,4] <- WAIC_compare_resid[1,1] %>% round(2)
Resid_compare_WAIC[2,4] <- WAIC_compare_resid[2,1] %>% round(2)

Resid_compare_WAIC[1,5] <- WAIC_compare_resid[1,2] %>% round(2)
Resid_compare_WAIC[2,5] <- WAIC_compare_resid[2,2] %>% round(2)

#LOO
Resid_compare_WAIC[1,4] <- WAIC_compare_resid[1,1] %>% round(2)
Resid_compare_WAIC[2,4] <- WAIC_compare_resid[2,1] %>% round(2)

Resid_compare_WAIC[1,5] <- WAIC_compare_resid[1,2] %>% round(2)
Resid_compare_WAIC[2,5] <- WAIC_compare_resid[2,2] %>% round(2)
```

```{r, eval = TRUE}
pander(Resid_compare_WAIC,
       justify = "lcccc",
       #split.cell = 80,
       caption = "Table SX Comparisons of LOO values for homogenous and hetergenous residuals")
```


```{r}
#Fixed effects model selection
cc_mod.2.obj <- readRDS("output/rds/cc_mod.2.obj")
cc_mod.3.obj <- readRDS("output/rds/cc_mod.3.obj")

#Add IC
waic_cc_mod.2.obj <- waic(cc_mod.2.obj)
loo_cc_mod.2.obj <- loo(cc_mod.2.obj)

waic_cc_mod.3.obj <- waic(cc_mod.3.obj)
loo_cc_mod.3.obj <- loo(cc_mod.3.obj)

loo_compare(waic_cc_mod.2.obj, waic_cc_mod.3.obj)
loo_compare(loo_cc_mod.2.obj, loo_cc_mod.3.obj)
```

```{r}
#Tabulate the model coefficients for CC model
#Read in model
cc_mod.3.obj <- readRDS("output/rds/cc_mod.3.obj")

summary(cc_mod.3.obj)

#Extract entire posterior
cc_mod.3_post <- posterior_samples(cc_mod.3.obj)
#Names of each column
colnames(cc_mod.3_post)[1:11]

#Combining the coefficients from the final model
#Getting the fixed effects
cc_mod.3_coeffs <- cc_mod.3_post[1:11] %>% posterior_summary() %>% round(3) 
#Excluding est. error
cc_mod.3_coeffs <- cc_mod.3_coeffs[,c(1,3,4)]
#Rownames as col
cc_mod.3_coeffs <- as.data.frame(cc_mod.3_coeffs)
cc_mod.3_coeffs$Parameter <- c(rownames(cc_mod.3_coeffs))
rownames(cc_mod.3_coeffs) <- NULL 
cc_mod.3_coeffs <- cc_mod.3_coeffs[,c(4,1:3)]
```

```{r}
pander(cc_mod.3_coeffs,
       justify = "lccc",
       #split.cell = 80,
       caption = "Table SX Model coefficients of full model testing whether developmental temperature affects the elevation and slope of the thermal reaction norm of metabolic rate. This model used a complete case dataset, n = 3818")
```

```{r}
#Tabulate the model coefficients for imp model
#Read in model
mod.imp.3.obj <- readRDS("output/rds/mod.imp.3")

summary(mod.imp.3.obj)

#Extract entire posterior
mod.imp.3_post <- posterior_samples(mod.imp.3.obj)
#Names of each column
colnames(mod.imp.3_post)[1:14]

#Combining the coefficients from the final model
#Getting the fixed effects
mod.imp.3_coeffs <- mod.imp.3_post[1:14] %>% posterior_summary() %>% round(3) 
#Excluding est. error
mod.imp.3_coeffs <- mod.imp.3_coeffs[,c(1,3,4)]
#Rownames as col
mod.imp.3_coeffs <- as.data.frame(mod.imp.3_coeffs)
mod.imp.3_coeffs$Parameter <- c(rownames(mod.imp.3_coeffs))
rownames(mod.imp.3_coeffs) <- NULL 
mod.imp.3_coeffs <- mod.imp.3_coeffs[,c(4,1:3)]
```

```{r}
cc_mod.3.obj <- readRDS("output/rds/cc_mod.3.obj")

#Make a figure from model predictions using cc_mod.2.obj
cc_mod.3.imp.post <- posterior_samples(cc_mod.3.obj) 
names(cc_mod.3.imp.post)[1:12]

#Setting up predictive data
new_data <- mi_data %>% distinct(id, samp_session, temp, treatment)

#Specificying the posterior
post = cc_mod.3.imp.post

#Try fucking pmap    
model_predictions <- bind_rows(pmap(new_data, mr_pred))
str(model_predictions)
rownames(model_predictions) <- NULL

#Check it
model_predictions %>% filter(id == "ld0449") #Fantastic

#Change ID to character
model_predictions %<>%  mutate(id = as.character(id))

#Plot it
cold_ids <- model_predictions %>% filter(treatment == 23) %>% pull(id) %>% unique()
hot_ids <- model_predictions %>% filter(treatment == 29) %>% pull(id) %>% unique()

set.seed(7)
subset_cold <- sample(cold_ids, 10 , replace = F)

set.seed(7)
subset_hot <- sample(hot_ids, 10 , replace = F)

#Filter out the subset IDS
model_predictions %>% filter(id %in% c(subset_cold, subset_hot) & samp_session %in% c(1,5,10)) %>% 
  ggplot(aes(x = temp, y = mean_lnmr)) + 
  geom_line(aes(group = id, colour = factor(treatment)), stat="smooth", method = "lm", lwd = 0.5, alpha = 0.5) + 
  geom_line(aes(group = factor(treatment), colour = factor(treatment)), stat="smooth", method = "lm", lwd = 2, alpha = 1, position=position_dodge(width = 0.3)) +
  geom_point(alpha = 0.2) + 
  facet_wrap(~samp_session) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) + 
  scale_x_continuous(breaks = c(seq(24,34, by = 2))) + 
  labs(x = "Temperature",
       y = TeX("log VCO_2 per minute"),
       #title = "Relative contribution of variance over age",
       colour =  "Treatment") + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none",
        strip.text = element_text(size = 18),
        strip.background = element_blank())

```

```{r, include = TRUE}
#Read in model
mod.imp.3.obj <- readRDS("output/rds/mod.imp.3")

#Make a figure from model predictions using mod.imp.3.obj
mod.3.imp.post <- posterior_samples(mod.imp.3.obj) 
names(mod.3.imp.post)[1:14]
names(mod.3.imp.post)[120:150]

#Specificying the posterior
post = mod.3.imp.post

#Try pmap
imp_model_predictions <- bind_rows(pmap(new_data, imp_mr_pred))
str(imp_model_predictions)
rownames(imp_model_predictions) <- NULL

#Check it
imp_model_predictions %>% filter(id == "ld0449" & samp_session == 1) #Fantastic
model_predictions %>% filter(id == "ld0449" & samp_session == 1)

#Filter out the subset IDS
imp_model_predictions %>% filter(id %in% c(subset_cold, subset_hot) & samp_session %in% c(1,5,10)) %>% 
  ggplot(aes(x = temp, y = mean_lnmr)) + 
  geom_line(aes(group = id, colour = factor(treatment)), stat="smooth", method = "lm", lwd = 0.5, alpha = 0.5) + 
  geom_line(aes(group = factor(treatment), colour = factor(treatment)), stat="smooth", method = "lm", lwd = 2, alpha = 1, position=position_dodge(width = 0.3)) +
  geom_point(alpha = 0.2) + 
  facet_wrap(~samp_session) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) + 
  scale_x_continuous(breaks = c(seq(24,34, by = 2))) + 
  labs(x = "Temperature",
       y = TeX("log VCO_2 per minute"),
       #title = "Relative contribution of variance over age",
       colour =  "Treatment") + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none",
        strip.text = element_text(size = 18),
        strip.background = element_blank())
```

```{r, include = TRUE, fig.height = 9.5, fig.width = 6.7}
#Treatment differences in temperature specific repeatabilty
# Read in models
cc_cold.2.obj <- readRDS("output/rds/cc_cold.2.obj")
cc_hot.2.obj <- readRDS("output/rds/cc_hot.2.obj")

#Poster names
names(posterior_samples(cc_cold.2.obj))[1:10]

#Function to calculate temperature specific repeatability
brms_rpt <- function(x, model){
    #Strings to search for relevant (co)variance components
    id_vars <- paste0("sd_","id")
    id_cors <- paste0("cor_","id")
    
    #Extract the relevant sd/(co)variance components for ID 
    SD <- posterior_samples(model, id_vars)
    COR <- posterior_samples(model, id_cors) 
    V <- SD^2
    names(V) <- str_replace(names(V), "sd", "var")
    #Convert correlation to covariance #Cor(1,2) * (SD1 X SD2) = Cov(1,2)
    COV <- cbind(COR[1] * (SD[1] * SD[2]))
    names(COV) <- str_replace(names(COV), "cor", "cov")
    
    # Now, add everything together while accounting for covariances and their respective powers
    V_id <- V[1] + (x^2)*V[2] +  #The V of the intercept and linear slope
      2*x*COV[1]    # Covariance of intercept and linear slope
    
    #Samp session variance
    #Strings to search for relevant (co)variance components
    ss_vars <- paste0("sd_samp")
    
    #Extract the relevant sd/(co)variance components 
    SD_SS <- posterior_samples(model, ss_vars)
    
    #Squaring SD to get the variance
    V_SS <- (SD_SS)^2 
    
    #Residuals
    SD_e <- posterior_samples(model, "sigma") # Extract the variance of intercept, linear slope
    
    #Squaring SD to get the variance
    V_resid <- (SD_e)^2 
    
    #Calculate total phenotypic variance
    VtotalP <- V_id + V_SS + V_resid 
    
    #    # Calculate repeatability (proportion of variance explained by consistent ID variance)
    R <- V_id  / VtotalP
    
    df <- data.frame(temp = x,
                     rpt = posterior_summary(R)[1] %>% round(2),
                     Lower =  posterior_summary(R)[3] %>% round(2),
                     Upper =  posterior_summary(R)[4] %>% round(2))

    return(df)
}

#map(new_data %>% select(temp) %>% distinct(), brms_rpt) #Can't get this to work

cold_rpt <- bind_rows(lapply(temp, function(x) brms_rpt(x, model = cc_cold.2.obj)))
cold_rpt %<>%  mutate(treatment = "cold")

hot_rpt <- bind_rows(lapply(temp, function(x) brms_rpt(x, model = cc_hot.2.obj)))
hot_rpt %<>%  mutate(treatment = "hot")

rpt_data <- bind_rows(cold_rpt, hot_rpt)

#plot this
ggplot(rpt_data, aes(x = factor(temp), y = rpt, group = treatment, colour = treatment)) + 
  geom_point(position = position_dodge(0.5), size = 4) + 
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0, position = position_dodge(0.5), size = 0.6) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) +
  ylim(c(0, 0.4)) + 
  labs(x = "Temperature",
       y = "Repeatability",
       colour =  "Treatment") + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none") 

```

```{r}
#Overall repeatability
overall_rpt <- bind_rows(lapply(temp, function(x) brms_rpt(x, model = cc_mod.3.obj)))
```

## How does developmental temperature affect temperature specific repeatability

Lizards born in cold developmental temperatures had on higher repeatabilty compared to lizards from the hot developmental temeprature however, credible intervals overlap partially (Fig. XX, Table XX). Across both treatment grounts, repeatability did not change across acute temperatures (Fig.2, Table XX).  
