---
title: "Results"
author: "Fonti Kar"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  word_document:
    reference_docx: Style_guide.docx
---

```{r setup, eval = TRUE, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(eval = FALSE,
                      echo = FALSE, 
                      include = FALSE, 
                      warning = FALSE,
                      message = FALSE)
rm(list=ls())
sessionInfo()

# R version 3.6.1 (2019-07-05)
# Platform: x86_64-apple-darwin15.6.0 (64-bit)
# Running under: macOS High Sierra 10.13.6

pacman::p_load(dplyr, magrittr, ggplot2, purrr, Rphylopars, phytools, GGally, mice, janitor, patchwork, GGally, psych, brms, mi, pander,latex2exp, stringr, tidybayes, bayestestR)

my_theme <- theme(#legend.position = "none",
  legend.position = "bottom",
  legend.text =element_text(size = 14),
  legend.title =element_text(size = 14, face = "bold"),
  panel.grid.major = element_blank(), 
  panel.grid.minor = element_blank(),
  axis.text=element_text(size=16),
  axis.title=element_text(size=16),
  plot.title = element_text(size = 20, face = "bold", hjust = 0.5),
  plot.background = element_rect(colour = "white"))

source("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/R/functions/helper.R")
```

$$I_{t} = V_{I} + (t^2.V_{S}) + (2t.Cov_{I,S}) $$

where $V_I$ is the among individual variance in intercepts, $t$ is the specific temperature at which repeatability is calculated for, $V_S$ is the among individual and $COV_{I,S}$ is the covariance between the intercept and slope at the among individual level. Temperature specific repeatability ($R_{t}$) is calculated as follows: 

$$R_{t} = \displaystyle \frac{I_{t}}{(I_{t} + V_{session} + V_{e})} $$

where: $I_{t}$ is the variance among individuals at a particular temperature, $V_{session}$ is the variance due to sampling session and $V_{e}$ is residual variance. 

$$R_{slope} = \displaystyle \frac{V_{I,slope}}{(V_{I,slope} + V_{series, slope})} $$
where: $V_{I,slope}$ is the among individual variance in the temperature slope term and the $V_{series, slope}$ is the among sampling session within individual variance in the temperature slope term

```{r, eval = TRUE}
## Read in data
data <-read.csv("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/data/processed/Long_Tinc_MR.csv", stringsAsFactors = F)
mi_data <-read.csv("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/data/processed/Long_Tinc_MR_MI.csv", stringsAsFactors = F)
```

```{r, eval = TRUE}
#Tabulate the model coefficients for imp model
#Read in model
mod.imp.z3 <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/mod.imp.z3")

#Extract entire posterior
mod.imp.3_post <- posterior_samples(mod.imp.z3)
#Names of each column
colnames(mod.imp.3_post)[1:14]

#Combining the coefficients from the final model
#Getting the fixed effects
mod.imp.3_fixed <- mod.imp.3_post[1:7] %>% posterior_summary() %>% round(3) 

#Getting the SD 
mod.imp.3_sd <- posterior_samples(mod.imp.z3, "sd_")
mod.imp.3_var <- mod.imp.3_sd^2 
names(mod.imp.3_var) <- str_replace(names(mod.imp.3_var), "sd", "var")
mod.imp.3_var %>% posterior_summary() %>% signif(3) 

#Getting the COR to cov
mod.imp.3_cov <- posterior_samples(mod.imp.z3, "cor_") * (mod.imp.3_sd[,1] * mod.imp.3_sd[,2])
names(mod.imp.3_cov) <- str_replace(names(mod.imp.3_cov), "cor", "cov")

mod.imp.3_cov %>% posterior_summary() %>% signif(3) 

#Getting the residuals
mod.imp.3_residuals <- ( posterior_samples(mod.imp.z3, "sigma")^2 ) %>% posterior_summary() %>% round(3) 

#Bind these together
mod.imp.3_coeffs <- rbind(mod.imp.3_fixed,
                              mod.imp.3_var %>% posterior_summary() %>% round(3),
                              mod.imp.3_cov %>% posterior_summary() %>% signif(3),
                              mod.imp.3_residuals)
        
#Excluding est. error
mod.imp.3_coeffs <- mod.imp.3_coeffs[,c(1,3,4)]
#Rownames as col
mod.imp.3_coeffs <- as.data.frame(mod.imp.3_coeffs)
mod.imp.3_coeffs$Parameter <- c(rownames(mod.imp.3_coeffs))
rownames(mod.imp.3_coeffs) <- NULL 
mod.imp.3_coeffs <- mod.imp.3_coeffs[,c(4,1:3)]
```

```{r, eval = TRUE, include = TRUE}
pander(mod.imp.3_coeffs,
       justify = "lccc",
       #split.cell = 80,
       caption = "Table 1 Model coefficients of full model testing whether developmental temperature affects the elevation and slope of the thermal reaction norm of metabolic rate. This model used an imputated dataset, n = 6000")
```

```{r, eval = TRUE, cache = TRUE}
#Read in model
mod.imp.3.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/mod.imp.3")

#Make a figure from model predictions using mod.imp.3.obj
mod.3.imp.post <- posterior_samples(mod.imp.3.obj) 
names(mod.3.imp.post)[1:14]
names(mod.3.imp.post)[120:150]

#Specificying the posterior
post = mod.3.imp.post

#Setting up predictive data
new_data <- mi_data %>% distinct(id, samp_session, temp, treatment)

#Try pmap
imp_model_predictions <- bind_rows(pmap(new_data, imp_mr_pred))
str(imp_model_predictions)
rownames(imp_model_predictions) <- NULL

#Check it
imp_model_predictions %>% filter(id == "ld0449" & samp_session == 1) #Fantastic

#Change ID to character
imp_model_predictions %<>%  mutate(id = as.character(id))

#Plot it
cold_ids <- imp_model_predictions %>% filter(treatment == 23) %>% pull(id) %>% unique()
hot_ids <- imp_model_predictions %>% filter(treatment == 29) %>% pull(id) %>% unique()

set.seed(7)
subset_cold <- sample(cold_ids, 10 , replace = F)

set.seed(7)
subset_hot <- sample(hot_ids, 10 , replace = F)
```

```{r, eval = TRUE, include = TRUE, fig.height = 6.7, fig.width = 9.5}
#Raw data for thermal reaction norms of each treatment
 data %>% filter(id %in% c(subset_cold, subset_hot)) %>% 
  ggplot(aes(x = temp, y = lnmr)) + 
  geom_line(aes(group = factor(treatment), colour = factor(treatment)), stat="smooth", method = "lm", lwd = 2, alpha =1) + 
geom_point(aes(group = factor(treatment), colour = factor(treatment)), alpha = 0.2) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) + 
  scale_x_continuous(breaks = c(seq(24,34, by = 2))) + 
  scale_y_continuous(lim = c(-7.2,-5.3)) + 
  labs(x = "Temperature",
       y = TeX("log VCO_2 mL min^{-1}"),
       #title = "Relative contribution of variance over age",
       colour =  "Treatment") + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none",
        strip.text = element_text(size = 18),
        strip.background = element_blank())

#Raw data for repeatability of slope
hot_col <- c("red3", "tomato2", "sienna1", "orangered", "chocolate1", 
             "indianred2", "sandybrown", "firebrick1", "darkred", "saddlebrown")

cold_col <- c("royalblue4", "cornflowerblue", "lightseagreen", "lightskyblue", "lightsteelblue3", 
             "cadetblue", "skyblue3", "skyblue4", "turquoise4", "steelblue1")

#HOT
raw_hot <- data %>% filter(treatment == 29 & samp_session %in% c(1,5,10)) %>% filter(id %in% c(subset_hot)) %>% 
  ggplot(aes(x = temp, y = lnmr)) + 
  geom_line(aes(group = id, colour = factor(id)), stat="smooth", method = "lm", lwd = 0.5, alpha =1) + 
  #geom_line(color = "#F24D2A", stat="smooth", method = "lm", lwd = 2, alpha = 0.7) +
  facet_wrap(~samp_session) + 
  scale_colour_manual(values = hot_col) + 
  scale_x_continuous(breaks = c(seq(24,34, by = 2))) + 
  scale_y_continuous(lim = c(-7.2,-5.3)) + 
  labs(x = " ",
       y = TeX("log VCO_2 mL min^{-1}"),
       #title = "Relative contribution of variance over age",
       colour =  "Treatment") + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none",
        strip.text = element_text(size = 18),
        strip.background = element_blank())

#COLD
raw_cold <- data %>% filter(id %in% subset_cold & samp_session %in% c(1,5,10)) %>% 
  ggplot(aes(x = temp, y = lnmr)) + 
  geom_line(aes(group = id, colour = factor(id)), stat="smooth", method = "lm", lwd = 0.5, alpha = 1) + 
  #geom_line(color = "#2790F3", stat="smooth", method = "lm", lwd = 2, alpha = 0.8) +
  facet_wrap(~samp_session) + 
  scale_colour_manual(values = cold_col) + 
  scale_x_continuous(breaks = c(seq(24,34, by = 2))) + 
  scale_y_continuous(lim = c(-7.2,-5.3)) + 
  labs(x = "Temperature",
       y = TeX("log VCO_2 mL min^{-1}"),
       #title = "Relative contribution of variance over age",
       colour =  "Treatment") + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none",
        strip.text = element_text(size = 18),
        strip.background = element_blank())
```

```{r}
plot_layout(raw_hot / raw_cold)
```

```{r}

#Extract average reaction norm for each treatment and get CI around them
mod.imp.z3 <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/mod.imp.z3")

#Extract entire posterior
mod.imp.3_post <- posterior_samples(mod.imp.z3)
post = mod.imp.3_post

#Names of each column
names(mod.imp.3_post)[1:14]

#Temp
temp = seq(24,34, by = 2)
z_temp = scale(temp)[,1]
#For Cold 
mod.3.imp.post["b_lnmr_Intercept"]

mean_24 <- (post["b_lnmr_Intercept"] +  #Intercept represents mean MR for cold
      post["b_lnmr_z_temp"] * z_temp[1] +   #Temperature effect 
      post["bsp_lnmr_miz_lnmass"] * 0 + #Mass effect * mean age
      post["b_lnmr_z_age"] * 0 + #Age effect + mean age
      post["sd_id__lnmr_Intercept"] + 
      post["sd_id__lnmr_z_temp"] * z_temp[1]  + 
      post["sd_samp_session__lnmr_Intercept"]) 

mean_26 <- post["b_lnmr_Intercept"] +  #Intercept represents mean MR for cold
    post["b_lnmr_z_temp"] * z_temp[2] +   #Temperature effect 
    post["bsp_lnmr_miz_lnmass"] * 0 + #Mass effect * mean age
    post["b_lnmr_z_age"] * 0 + #Age effect + mean age
    post["sd_id__lnmr_Intercept"] + 
    post["sd_id__lnmr_z_temp"] * z_temp[2] + 
    post["sd_samp_session__lnmr_Intercept"]

mean_28 <- post["b_lnmr_Intercept"] +  #Intercept represents mean MR for cold
  post["b_lnmr_z_temp"] * z_temp[3] +   #Temperature effect 
  post["bsp_lnmr_miz_lnmass"] * 0 + #Mass effect * mean age
  post["b_lnmr_z_age"] * 0 + #Age effect + mean age
  post["sd_id__lnmr_Intercept"] + 
  post["sd_id__lnmr_z_temp"] * z_temp[3] + 
  post["sd_samp_session__lnmr_Intercept"]

mean_30 <- post["b_lnmr_Intercept"] +  #Intercept represents mean MR for cold
  post["b_lnmr_z_temp"] * z_temp[4] +   #Temperature effect 
  post["bsp_lnmr_miz_lnmass"] * 0 + #Mass effect * mean age
  post["b_lnmr_z_age"] * 0 + #Age effect + mean age
  post["sd_id__lnmr_Intercept"] + 
  post["sd_id__lnmr_z_temp"] * z_temp[4] + 
  post["sd_samp_session__lnmr_Intercept"]

mean_32 <- post["b_lnmr_Intercept"] +  #Intercept represents mean MR for cold
  post["b_lnmr_z_temp"] * z_temp[5] +   #Temperature effect 
  post["bsp_lnmr_miz_lnmass"] * 0 + #Mass effect * mean age
  post["b_lnmr_z_age"] * 0 + #Age effect + mean age
  post["sd_id__lnmr_Intercept"] + 
  post["sd_id__lnmr_z_temp"] * z_temp[5] + 
  post["sd_samp_session__lnmr_Intercept"]

mean_34 <- post["b_lnmr_Intercept"] +  #Intercept represents mean MR for cold
  post["b_lnmr_z_temp"] * z_temp[6] +   #Temperature effect 
  post["bsp_lnmr_miz_lnmass"] * 0 + #Mass effect * mean age
  post["b_lnmr_z_age"] * 0 + #Age effect + mean age
  post["sd_id__lnmr_Intercept"] + 
  post["sd_id__lnmr_z_temp"] * z_temp[6] + 
  post["sd_samp_session__lnmr_Intercept"]

cold_fixed_pred <- rbind(posterior_summary(mean_24),
                    posterior_summary(mean_26),
                    posterior_summary(mean_28),
                    posterior_summary(mean_30),
                    posterior_summary(mean_32),
                    posterior_summary(mean_34)) %>% as.data.frame()

cold_fixed_pred %<>% mutate(temp = seq(24,34, by = 2),
                            Treatment = "Cold")

cold_fixed_pred %<>% rename(Lower = Q2.5,
                       Upper = Q97.5,
                       Temperature = temp)

#For Hot
mean_24_hot <- mean_24 + post[,"b_lnmr_treatment29"] * 1 + 
  post[,"b_lnmr_treatment29:z_temp"] * 1

mean_26_hot <- mean_26 + post[,"b_lnmr_treatment29"] * 1 + 
  post[,"b_lnmr_treatment29:z_temp"] * 1

mean_28_hot <- mean_28 + post[,"b_lnmr_treatment29"] * 1 + 
  post[,"b_lnmr_treatment29:z_temp"] * 1

mean_30_hot <- mean_30 + post[,"b_lnmr_treatment29"] * 1 + 
  post[,"b_lnmr_treatment29:z_temp"] * 1

mean_32_hot <- mean_32 + post[,"b_lnmr_treatment29"] * 1 + 
  post[,"b_lnmr_treatment29:z_temp"] * 1

mean_34_hot <- mean_34 + post[,"b_lnmr_treatment29"] * 1 + 
  post[,"b_lnmr_treatment29:z_temp"] * 1

hot_fixed_pred <- rbind(posterior_summary(mean_24_hot),
                        posterior_summary(mean_26_hot),
                        posterior_summary(mean_28_hot),
                        posterior_summary(mean_30_hot),
                        posterior_summary(mean_32_hot),
                        posterior_summary(mean_34_hot)) %>% as.data.frame()

hot_fixed_pred %<>% mutate(temp = seq(24,34, by = 2),
                           Treatment = "Hot")

hot_fixed_pred %<>% rename(Lower = Q2.5,
                            Upper = Q97.5,
                            Temperature = temp)

#Bind together
fixed_pred <- bind_rows(hot_fixed_pred, cold_fixed_pred)

#Plot together
ggplot() + 
  geom_point(data = data, aes(x = temp, y = lnmr, group = factor(treatment), colour = factor(treatment)), alpha = 0.05) +
  geom_point(data = fixed_pred, aes(x = Temperature, y = Estimate, colour = Treatment), size = 2) + 
  geom_line(data = fixed_pred, aes(x = Temperature, y = Estimate, colour = Treatment), size = 1.2) +
  geom_ribbon(data = fixed_pred, aes(x = Temperature, y = Estimate, ymin = Lower, ymax = Upper, colour = Treatment), alpha = 0.05, linetype = "dashed") +
  scale_colour_manual(values = c("#2790F3", "#F24D2A", "#2790F3", "#F24D2A")) + 
  scale_x_continuous(breaks = c(seq(24,34, by = 2))) + 
  scale_y_continuous(lim = c(-7.2,-5.3)) + 
  labs(x = "Temperature",
       y = TeX("log VCO_2 mL min^{-1}"),
       #title = "Relative contribution of variance over age",
       colour =  "Treatment") + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none",
        strip.text = element_text(size = 18),
        strip.background = element_blank())
```


```{r}
#Repeatability of the slope for each treatment
#Imputed
cold.mod.imp.4 <- readRDS("output/rds/cold.mod.imp.z4")
hot.mod.imp.4 <- readRDS("output/rds/hot.mod.imp.z4")

brms_rptSlope_imp(model = cold.mod.imp.4, transform = "z", type = "mean")
brms_rptSlope_imp(model = hot.mod.imp.4, transform = "z", type = "mean")

#Test for differences in repeatability of slope
RslopeCold <-brms_rptSlope_imp(model = cold.mod.imp.4, transform = "z", type = "posterior")
RslopeHot <- brms_rptSlope_imp(model = hot.mod.imp.4, transform = "z", type = "posterior")

RslopeDiff <- RslopeHot - RslopeCold
rope(RslopeDiff, ci = 0.95)
plot(p_direction(RslopeDiff))
((1- 0.5355) / 100)*2

pdslopediff <- p_direction(RslopeDiff)
pd_to_p(0.5355, direction = "two-sided")
(1- 0.5355)*2
```

```{r, eval = TRUE}
#Treatment differences in temperature specific repeatabilty using imputation models
# Read in models
cold_imp.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/cold.mod.imp.3.z")
hot_imp.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/hot.mod.imp.3.z")

#Poster names
names(posterior_samples(cold_imp.obj))[1:10]

#Temp define:
temp <- seq(24,34, by = 2)
z_temps <- scale(temp)[,1]
# map(temp, 
#     brms_rpt_imp) #Can't get this to work

imp_cold_rpt <- bind_rows(lapply(z_temps, function(x) brms_rpt_imp(x, model = cold_imp.obj)))
imp_cold_rpt %<>%  mutate(treatment = "cold")

imp_hot_rpt <- bind_rows(lapply(z_temps, function(x) brms_rpt_imp(x, model = hot_imp.obj)))
imp_hot_rpt %<>%  mutate(treatment = "hot")

imp_rpt_data <- bind_rows(imp_cold_rpt, imp_hot_rpt)
imp_rpt_data %<>% mutate(temp = rep(seq(24,34, by = 2), 2))
```

```{r, eval = TRUE, include = TRUE, fig.height = 6.7, fig.width = 9.5, cache = TRUE}
#Fig 2
adjs_rpt <- ggplot(imp_rpt_data, aes(x = factor(temp), y = rpt, group = treatment, colour = treatment)) + 
  geom_point(position = position_dodge(0.5), size = 4) + 
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0, position = position_dodge(0.5), size = 0.6) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) +
  ylim(c(0, 0.4)) + 
  labs(x = "Temperature",
       y = "Repeatability",
       colour =  "Treatment") + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none") 

adjs_rpt
```

```{r}
imp_a <- ggplot(imp_rpt_data, aes(x = factor(temp), y = rpt, group = treatment, colour = treatment)) + 
  geom_point(position = position_dodge(0.5), size = 4) + 
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0, position = position_dodge(0.5), size = 0.6) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) +
  ylim(c(0, 0.26)) + 
  labs(x = "Temperature",
       y = "Repeatability",
       colour =  "Treatment") + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none") 

imp_b <- ggplot(imp_rpt_mode, aes(x = factor(temp), y = rpt, group = treatment, colour = treatment)) + 
  geom_point(position = position_dodge(0.5), size = 4) + 
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0, position = position_dodge(0.5), size = 0.6) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) +
  ylim(c(0, 0.26)) + 
  labs(x = "Temperature",
       y = "Repeatability",
       colour =  "Treatment") + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none") 

plot_layout(imp_a / imp_b)
```

```{r, eval = TRUE, include= TRUE}
#Tabulating repeatability at each temperature
imp_rpt_data %<>% select(treatment, temp:Upper)

pander(imp_rpt_data,
       justify = "lcccc",
       #split.cell = 80,
       caption = "Table 2 Temeprature specific, adjusted repeatability estimates of log transformed metabolic rate for lizards from two developmental temperatures (n_hot = 25, n_cold = 26). These values were estimated from an imputation analysis, n_obs = 6000")
```

```{r}
#Are there actually any significant differences in T specific repeatability of average MR? Test properly with bayestestR
temp <- seq(24,34, by = 2)
z_temps <- scale(temp)[,1]

diff_24 <- rpt_posterior(x = z_temps[1], model = hot_imp.obj) - rpt_posterior(x = z_temps[1], model = cold_imp.obj)
diff_24_df <- posterior_summary(diff_24) %>% round(3)
p_direction(diff_24)
p_direction(diff_24) %>%  plot()
((1 - p_direction(diff_24)$pd[1]))*2
pd_to_p(p_direction(diff_24)$pd[1], direction = "two-sided")
pd_to_p(p_direction(diff_24)$pd[1], direction = "one-sided")


diff_26 <- rpt_posterior(x = z_temps[2], model = hot_imp.obj) - rpt_posterior(x = z_temps[2], model = cold_imp.obj)
diff_26_df <- posterior_summary(diff_26) %>% round(3)
p_direction(diff_26)
((1 - p_direction(diff_26)$pd[1] ))*2

diff_28 <- rpt_posterior(x = z_temps[3], model = hot_imp.obj) - rpt_posterior(x = z_temps[3], model = cold_imp.obj)
diff_28_df <- posterior_summary(diff_28) %>% round(3)
p_direction(diff_28)
((1 - p_direction(diff_28)$pd[1] ))*2

diff_30 <- rpt_posterior(x = z_temps[4], model = hot_imp.obj) - rpt_posterior(x = z_temps[4], model = cold_imp.obj)
diff_30_df <- posterior_summary(diff_30) %>% round(3)
p_direction(diff_30)
((1 - p_direction(diff_30)$pd[1] ))*2

diff_32 <- rpt_posterior(x = z_temps[5], model = hot_imp.obj) - rpt_posterior(x = z_temps[5], model = cold_imp.obj)
diff_32_df <- posterior_summary(diff_32) %>% round(3)
p_direction(diff_32)
((1 - p_direction(diff_32)$pd[1]))*2

diff_34 <- rpt_posterior(x = z_temps[6], model = hot_imp.obj) - rpt_posterior(x = z_temps[6], model = cold_imp.obj)
diff_34_df <- posterior_summary(diff_34) %>% round(3)
p_direction(diff_34)
((1 - p_direction(diff_34)$pd[1])*2)

#Compile the posteriors together
contrast_df <- cbind(diff_24,
                     diff_26,
                     diff_28,
                     diff_30,
                     diff_30,
                     diff_34) %>% as.data.frame()

names(contrast_df) <- c("24", "26", "28", "30", "32", "34")
```

```{r}
#Repeatability overall between developmental temperature groups
#Read in models
hot.mod.imp.5.z <- readRDS("output/rds/hot.mod.imp.5.z")
cold.mod.imp.5.z <- readRDS("output/rds/cold.mod.imp.5.z")

posterior_samples(hot.mod.imp.5.z)[,1:10] %>% names()

#Calculate adjusted repeatability overall
hot_post_5 <- posterior_samples(hot.mod.imp.5.z)
cold_post_5 <- posterior_samples(cold.mod.imp.5.z)

hot_overall_repeatability <- hot_post_5[,"sd_id__lnmr_Intercept"]^2 / (hot_post_5[,"sd_id__lnmr_Intercept"]^2 + hot_post_5[,"sd_samp_session__lnmr_Intercept"]^2 + hot_post_5[,"sigma_lnmr"]^2) 

cold_overall_repeatability <- cold_post_5[,"sd_id__lnmr_Intercept"]^2 / (cold_post_5[,"sd_id__lnmr_Intercept"]^2 + cold_post_5[,"sd_samp_session__lnmr_Intercept"]^2 + cold_post_5[,"sigma_lnmr"]^2) 

posterior_summary(hot_overall_repeatability) %>% round(3)
posterior_summary(cold_overall_repeatability) %>% round(3)

#Testing the contrast
posterior_summary(hot_overall_repeatability - cold_overall_repeatability) %>% round(3)

#Try out bayestestR
#Test whether the difference is signficantly diff from zero
rope_range(hot_overall_repeatability - cold_overall_repeatability)

rope(hot_overall_repeatability - cold_overall_repeatability, range = rope_range(hot_overall_repeatability - cold_overall_repeatability),ci=0.89)

diff <-  hot_overall_repeatability - cold_overall_repeatability
diff[diff > 0] %>%  length() / length(hot_overall_repeatability)
p_direction(diff)
plot(p_direction(diff))


#Compile in dataframe to maybe a piechart
marg_dat <- rbind(posterior_summary(hot_overall_repeatability),
                  posterior_summary(cold_overall_repeatability)) %>% as.data.frame()

marg_dat$treatment = NA
marg_dat[1,5] <- "Hot"
marg_dat[2,5] <- "Cold"

#Plot barcharts
overall <- ggplot(data = marg_dat, aes(x = treatment, y = Estimate)) + 
  geom_col(aes(fill = treatment)) + 
  geom_errorbar(aes(ymin = Q2.5, ymax = Q97.5), width = 0.1, size = 0.5) + 
  scale_fill_manual(values = c("#2790F3", "#F24D2A")) + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

#Compile data for violins (entire posterior)
vio_dat <- bind_cols(cold_overall_repeatability, hot_overall_repeatability) %>% as.data.frame()
vio_dat %<>% rename("Cold" = ...1, 
                   "Hot" = ...2)
vio_dat_long <- tidyr::pivot_longer(vio_dat, Cold:Hot, names_to = "Treatment", values_to = "Repeatability") %>% arrange(Treatment) 

vio_overall <- ggplot(data = vio_dat_long, aes(x = Treatment, y = Repeatability)) + 
  geom_violin(aes(fill = Treatment), trim = F) + 
  geom_jitter(shape=16, position=position_jitter(0.1), color = "black", alpha = 0.1) +
  # stat_summary(fun.data=mean_sdl, mult=1, 
  #                geom="pointrange", colour = "white") + 
  geom_boxplot(fill="black", colour = "white",
            outlier.shape=NA, width = 0.05, alpha = 0.6) +
  scale_fill_manual(values = c("#2790F3", "#F24D2A")) + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank())


#Plot the contrast
contrast_all <- bind_cols(contrast_df, hot_overall_repeatability - cold_overall_repeatability)
contrast_all %<>% rename(Overall = ...7)

#Pivot long
contrast_long <- tidyr::pivot_longer(contrast_all, cols = 1:7, names_to ="Temperature", values_to = "Diff_Repeatability") %>% arrange(Temperature)


#Set order 
contrast_long$Temperature <- factor(contrast_long$Temperature, levels = c("Overall", "34", "32","30", "28","26", "24"  ))


ggplot(contrast_long, aes(x = Temperature, y = Diff_Repeatability)) + 
  stat_halfeye(aes(fill = Temperature, colour = Temperature)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  coord_flip() +
  scale_fill_manual(values = c("black", rep("grey", 6))) +
  scale_colour_manual(values = c("grey", rep("black", 6)))+
  theme_bw() +
  labs(x = "",
       y = "Difference in Repeatability\n (Hot - Cold)") + 
  my_theme + 
  theme(legend.position = "none") +
  theme(legend.position = "none",
        axis.title.y = element_blank())

contrast <- ggplot(contrast_long, aes(x = Temperature, y = Diff_Repeatability)) + 
  stat_halfeye(aes(fill = stat(y < 0), shape = Temperature)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  coord_flip() +
  scale_fill_manual(values = c("grey12","grey")) +
  scale_shape_manual(values = c(23, 16, 16, 16, 16, 16, 16)) +
  theme_bw() +
  labs(x = "",
       y = "Difference in Repeatability\n (Hot - Cold)") + 
  my_theme + 
  theme(legend.position = "none") +
  theme(legend.position = "none",
        axis.title.y = element_blank())

  # ggplot(contrast_long, aes(x = temp, y = Estimate)) + 
  # geom_point(aes(shape = temp), size = c(4,4,4,4,4,4,6), fill = "black") + 
  # geom_errorbar(aes(ymin = Q2.5, ymax = Q97.5), width = 0, size = 0.6) + 
  # geom_hline(yintercept = 0, linetype = "dashed") +
  # ylim(c(-0.4, 0.25)) + 
  # scale_shape_manual(values = c(23, 16, 16, 16, 16, 16, 16 )) +
  # labs(x = "",
  #      y = "Difference in Repeatability\n (Hot - Cold)") + 
  # coord_flip() + 
  # theme_bw() +
  # my_theme + 
  # theme(legend.position = "none") +
  #   theme(legend.position = "none",
  #       axis.title.y = element_blank())
```


```{r}
#Combined model and testing differences in overall repeatability
cc_mod.combined.2.het.obj <- readRDS("output/rds/cc_mod.combined.2.het.obj")

#What is the repeatability overall for each treatment
comb_post <- posterior_samples(cc_mod.combined.2.het.obj)
names(comb_post)[1:11]

#Hot
(comb_post[,"sd_id__Intercept:treatment29"]^2 / (comb_post[,"sd_id__Intercept:treatment29"]^2  + comb_post[,"b_sigma_Intercept"]^2  + comb_post[,"b_sigma_treatment29"]^2)) %>% posterior_summary() %>% round(3)

#Cold
(comb_post[,"sd_id__Intercept:treatment23"]^2 / (comb_post[,"sd_id__Intercept:treatment23"]^2  + comb_post[,"b_sigma_Intercept"]^2)) %>% posterior_summary() %>% round(3)


#Hypothesis testing
h <- paste("sd_id__Intercept:treatment29^2 / (sd_id__Intercept:treatment29^2 +",
           "b_sigma_Intercept^2 + b_sigma_treatment29^2) > 0")
(hyp2 <- hypothesis(cc_mod.combined.2.het.obj, h, class = NULL))
plot(hyp2)

h2 <- paste("sd_id__Intercept:treatment23^2 / (sd_id__Intercept:treatment23^2 +",
           "b_sigma_Intercept^2) > 0")
(hyp3 <- hypothesis(cc_mod.combined.2.het.obj, h2, class = NULL))
plot(hyp2)


h3 <- paste("sd_id__Intercept:treatment23^2 / (sd_id__Intercept:treatment23^2 +",
           "b_sigma_Intercept^2) > sd_id__Intercept:treatment29^2 / (sd_id__Intercept:treatment29^2 +",
           "b_sigma_Intercept^2 + b_sigma_treatment29^2)")
(hyp4 <- hypothesis(cc_mod.combined.2.het.obj, h3, class = NULL))
plot(hyp4)
```

```{r}
#Investigating the among and residual variance
# Read in models
cold_imp.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/cold.mod.imp.3.z")
hot_imp.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/hot.mod.imp.3.z")

temp <- seq(24,34, by = 2)
z_temps <- scale(temp)[,1]

var_comp_cold <- bind_rows(lapply(z_temps, function(x) var_comp_imp(x, model = cold_imp.obj, var_comp = "id")))
var_comp_cold %<>%  mutate(treatment = "cold",
                           temp = seq(24,34, by = 2))

var_comp_hot <- bind_rows(lapply(z_temps, function(x) var_comp_imp(x, model = hot_imp.obj, var_comp = "id")))
var_comp_hot %<>%  mutate(treatment = "hot",
                          temp = seq(24,34, by = 2))

var_comps <- bind_rows(var_comp_cold, var_comp_hot)

#Overall
#Read in models
hot.mod.imp.5.z <- readRDS("output/rds/hot.mod.imp.5.z")
cold.mod.imp.5.z <- readRDS("output/rds/cold.mod.imp.5.z")

#Actual values
posterior_samples(hot.mod.imp.5.z, "sd_id") %>% posterior_summary() %>% round(3)
posterior_samples(cold.mod.imp.5.z, "sd_id") %>% posterior_summary() %>% round(3)

#Imputed
mod.imp.het.comb <- readRDS("output/rds/mod.imp.het.comb")

#Actual values
posterior_samples(mod.imp.het.comb, "sd_id") %>% posterior_summary() %>% round(3) #among id
posterior_samples(mod.imp.het.comb, "sigma") %>% posterior_summary() %>% round(3) #residual

amid_post <- bind_cols(posterior_samples(mod.imp.het.comb, "sd_id__lnmr_Intercept:treatment23")^2,
posterior_samples(mod.imp.het.comb, "sd_id__lnmr_Intercept:treatment29")^2) 
names(amid_post) <- c("Cold", "Hot")
amid_post_long <- tidyr::pivot_longer(amid_post, Cold:Hot, names_to = "Treatment", values_to = "Among ID Variance") %>% arrange(Treatment) 

sigma_post <- bind_cols(posterior_samples(mod.imp.het.comb, "b_sigma_lnmr_Intercept")^2,
(posterior_samples(mod.imp.het.comb, "b_sigma_lnmr_Intercept") + posterior_samples(mod.imp.het.comb, "sd_id__lnmr_Intercept:treatment29"))^2) 
names(sigma_post) <- c("Cold", "Hot")
sigma_post_long <- tidyr::pivot_longer(sigma_post, Cold:Hot, names_to = "Treatment", values_to = "Residual") %>% arrange(Treatment) 

#Put together
var_comp_compare <- bind_cols(amid_post_long, sigma_post_long[,2])
names(var_comp_compare)
var_comp_compare_long <- tidyr::pivot_longer(var_comp_compare, 2:3, names_to = "Type", values_to = "Variance") %>% arrange(Treatment) 

#Plot
#vio_overall <- 
ggplot(data = var_comp_compare_long, aes(x = Treatment, y = Variance)) + 
  geom_violin(aes(fill = Treatment), trim = F) + 
  geom_jitter(shape=16, position=position_jitter(0.1), color = "black", alpha = 0.1) +
  # stat_summary(fun.data=mean_sdl, mult=1, 
  #                geom="pointrange", colour = "white") + 
  geom_boxplot(fill="black", colour = "white",
               outlier.shape=NA, width = 0.05, alpha = 0.6) +
  scale_fill_manual(values = c("#2790F3", "#F24D2A")) + 
  facet_wrap(~Type, scales = "free") + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

#Diff AMID
AID_diff <- posterior_samples(hot.mod.imp.5.z, "sd_id") - posterior_samples(cold.mod.imp.5.z, "sd_id")
p_direction(AID_diff)

#Diff residual
sigma_diff <- (posterior_samples(mod.imp.het.comb, "b_sigma_lnmr_Intercept")^2 - (posterior_samples(mod.imp.het.comb, "b_sigma_lnmr_Intercept")^2 + posterior_samples(mod.imp.het.comb, "sd_id__lnmr_Intercept:treatment29")^2))
p_direction(sigma_diff) %>% plot()
```

```{r}
#Put figures in a panel
plot_layout(adjs_rpt + vio_overall/contrast)

#plot_layout(adjs_rpt + overall/contrast)
```

## How does developmental temperature affect temperature specific repeatability

Across both treatment grounts, repeatability did not change across acute temperatures (Fig.2, Table XX). There were no differences in repeatability between developmental temperatures (Fig. 2, Table XX). Although in the complete case analysis there was a trend for the cold developmental temperatures to have on higher repeatabilty compared to the hot developmental temeprature however credible intervals overlapped partially (Fig. XX, Table XX) and this result was not reflected in the more conservative imputation analysis. The slope of the thermal reaction norm was repeatable in both treatment groups, however there were no treatment differences (Fig. XX and). This result should be interpretted with caution as repeatability of the slope was estimated with a large degree of uncertainty (95% CI) 
