---
title: "Results"
author: "Fonti Kar"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  word_document:
    reference_docx: Style_guide.docx
---

```{r setup, eval = TRUE, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(eval = FALSE,
                      echo = FALSE, 
                      include = FALSE, 
                      warning = FALSE,
                      message = FALSE)
rm(list=ls())
sessionInfo()

# R version 3.6.1 (2019-07-05)
# Platform: x86_64-apple-darwin15.6.0 (64-bit)
# Running under: macOS High Sierra 10.13.6

pacman::p_load(dplyr, magrittr, ggplot2, purrr, Rphylopars, phytools, GGally, mice, janitor, patchwork, GGally, psych, brms, mi, pander,latex2exp, stringr)

my_theme <- theme(#legend.position = "none",
  legend.position = "bottom",
  legend.text =element_text(size = 14),
  legend.title =element_text(size = 14, face = "bold"),
  panel.grid.major = element_blank(), 
  panel.grid.minor = element_blank(),
  axis.text=element_text(size=16),
  axis.title=element_text(size=16),
  plot.title = element_text(size = 20, face = "bold", hjust = 0.5),
  plot.background = element_rect(colour = "white"))

source("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/R/functions/helper.R")
```

```{r, eval = TRUE}
## Read in data
data <-read.csv("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/data/processed/Long_Tinc_MR.csv", stringsAsFactors = F)
mi_data <-read.csv("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/data/processed/Long_Tinc_MR_MI.csv", stringsAsFactors = F)
```

## Heterogenous variance 
Model with homogenous variance was best supported by WAIC values. As such, we did not explicitly model residuals in all subsequent models
```{r, eval = TRUE}
mod.4.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/mod.4.obj") #Intercept ME HOMO
mod.4.het.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/mod.4.het.obj") #Intercept ME Hetero

#Add IC
waic_mod.4.obj<- waic(mod.4.obj)

waic_mod.4.het.obj <- waic(mod.4.het.obj)

#Compare
WAIC_compare_resid <- loo_compare(waic_mod.4.obj, waic_mod.4.het.obj)

#Creating table
Resid_compare_WAIC <- data.frame(matrix(nrow = 2, ncol = 4))
colnames(Resid_compare_WAIC) <- c("Model", "WAIC value", "ELPD Diff", "SE Diff")
Resid_compare_WAIC$Model <- c("Homogenous residuals", "Heterogenous residuals")

#WAIC
Resid_compare_WAIC[1,2] <- waic_mod.4.obj$estimates[3,1] %>% round(2)
Resid_compare_WAIC[2,2] <- waic_mod.4.het.obj$estimates[3,1] %>% round(2)

#ELPD and SE
#WAIC
Resid_compare_WAIC[1,3] <- WAIC_compare_resid[1,1] %>% round(2)
Resid_compare_WAIC[2,3] <- WAIC_compare_resid[2,1] %>% round(2)

Resid_compare_WAIC[1,4] <- WAIC_compare_resid[1,2] %>% round(2)
Resid_compare_WAIC[2,4] <- WAIC_compare_resid[2,2] %>% round(2)

```

```{r, eval = TRUE, include = TRUE}
pander(Resid_compare_WAIC,
       justify = "lcccc",
       #split.cell = 80,
       caption = "Table SX Comparisons of WAIC values for homogenous and hetergenous residuals")
```

```{r}
#Fixed effects model selection
cc_mod.1.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/cc_mod.1.obj")
cc_mod.2.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/cc_mod.2.obj")
cc_mod.3.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/cc_mod.3.obj")

#Add IC
waic_cc_mod.1.obj <- waic(cc_mod.1.obj)
waic_cc_mod.2.obj <- waic(cc_mod.2.obj)
waic_cc_mod.3.obj <- waic(cc_mod.3.obj)

loo_compare(waic_cc_mod.1.obj, waic_cc_mod.2.obj, waic_cc_mod.3.obj)
```

```{r, eval = TRUE}
#Tabulate the model coefficients for all CC model
#Read in models
cc_mod.1.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/cc_mod.1.obj")
cc_mod.3.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/cc_mod.3.obj")

#Model without interaction
#Extract entire posterior
cc_mod.1_post <- posterior_samples(cc_mod.1.obj)
#Names of each column
colnames(cc_mod.1_post)[1:11]

#Combining the coefficients from the final model
#Getting the fixed effects
cc_mod.1_coeffs <- cc_mod.1_post[1:11] %>% posterior_summary() %>% round(3) 
#Excluding est. error
cc_mod.1_coeffs <- cc_mod.1_coeffs[,c(1,3,4)]
#Rownames as col
cc_mod.1_coeffs <- as.data.frame(cc_mod.1_coeffs)
cc_mod.1_coeffs$Parameter <- c(rownames(cc_mod.1_coeffs))
rownames(cc_mod.1_coeffs) <- NULL 
cc_mod.1_coeffs <- cc_mod.1_coeffs[,c(4,1:3)]

#Full model
#Extract entire posterior
cc_mod.3_post <- posterior_samples(cc_mod.3.obj)
#Names of each column
colnames(cc_mod.3_post)[1:12]

#Combining the coefficients from the final model
#Getting the fixed effects
cc_mod.3_coeffs <- cc_mod.3_post[1:12] %>% posterior_summary() %>% round(3) 
#Excluding est. error
cc_mod.3_coeffs <- cc_mod.3_coeffs[,c(1,3,4)]
#Rownames as col
cc_mod.3_coeffs <- as.data.frame(cc_mod.3_coeffs)
cc_mod.3_coeffs$Parameter <- c(rownames(cc_mod.3_coeffs))
rownames(cc_mod.3_coeffs) <- NULL 
cc_mod.3_coeffs <- cc_mod.3_coeffs[,c(4,1:3)]
```

```{r, eval = TRUE, include = TRUE}
pander(cc_mod.1_coeffs,
       justify = "lccc",
       #split.cell = 80,
       caption = "Table SX Model coefficients of full model testing whether developmental temperature affects the elevation and slope of the thermal reaction norm of metabolic rate. This model used a complete case dataset, n = 3818")

pander(cc_mod.3_coeffs,
       justify = "lccc",
       #split.cell = 80,
       caption = "Table SX Model coefficients of full model testing whether developmental temperature affects the elevation and slope of the thermal reaction norm of metabolic rate. This model used a complete case dataset, n = 3818")
```

```{r, eval = TRUE}
#Tabulate the model coefficients for imp model
#Read in model
mod.imp.3.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/mod.imp.3")

#Extract entire posterior
mod.imp.3_post <- posterior_samples(mod.imp.3.obj)
#Names of each column
colnames(mod.imp.3_post)[1:14]

#Combining the coefficients from the final model
#Getting the fixed effects
mod.imp.3_coeffs <- mod.imp.3_post[1:14] %>% posterior_summary() %>% round(3) 
#Excluding est. error
mod.imp.3_coeffs <- mod.imp.3_coeffs[,c(1,3,4)]
#Rownames as col
mod.imp.3_coeffs <- as.data.frame(mod.imp.3_coeffs)
mod.imp.3_coeffs$Parameter <- c(rownames(mod.imp.3_coeffs))
rownames(mod.imp.3_coeffs) <- NULL 
mod.imp.3_coeffs <- mod.imp.3_coeffs[,c(4,1:3)]
```

```{r, eval = TRUE, include = TRUE}
pander(mod.imp.3_coeffs,
       justify = "lccc",
       #split.cell = 80,
       caption = "Table SX Model coefficients of full model testing whether developmental temperature affects the elevation and slope of the thermal reaction norm of metabolic rate. This model used an imputated dataset, n = 6000")
```

```{r, eval = TRUE, cache = TRUE}
cc_mod.3.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/cc_mod.3.obj")

#Make a figure from model predictions using cc_mod.2.obj
cc_mod.3.imp.post <- posterior_samples(cc_mod.3.obj) 
names(cc_mod.3.imp.post)[1:12]

#Setting up predictive data
new_data <- mi_data %>% distinct(id, samp_session, temp, treatment)

#Specificying the posterior
post = cc_mod.3.imp.post

#Try fucking pmap    
model_predictions <- bind_rows(pmap(new_data, mr_pred))
str(model_predictions)
rownames(model_predictions) <- NULL

#Check it
model_predictions %>% filter(id == "ld0449") #Fantastic

#Change ID to character
model_predictions %<>%  mutate(id = as.character(id))

#Plot it
cold_ids <- model_predictions %>% filter(treatment == 23) %>% pull(id) %>% unique()
hot_ids <- model_predictions %>% filter(treatment == 29) %>% pull(id) %>% unique()

set.seed(7)
subset_cold <- sample(cold_ids, 10 , replace = F)

set.seed(7)
subset_hot <- sample(hot_ids, 10 , replace = F)
```

```{r, eval = TRUE, include = TRUE, fig.height = 6.7, fig.width = 9.5}
#Filter out the subset IDS
model_predictions %>% filter(id %in% c(subset_cold, subset_hot) & samp_session %in% c(1,5,10)) %>% 
  ggplot(aes(x = temp, y = mean_lnmr)) + 
  geom_line(aes(group = id, colour = factor(treatment)), stat="smooth", method = "lm", lwd = 0.5, alpha = 0.5) + 
  geom_line(aes(group = factor(treatment), colour = factor(treatment)), stat="smooth", method = "lm", lwd = 2, alpha = 1, position=position_dodge(width = 0.3)) +
  geom_point(alpha = 0.2) + 
  facet_wrap(~samp_session) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) + 
  scale_x_continuous(breaks = c(seq(24,34, by = 2))) + 
  labs(x = "Temperature",
       y = TeX("log VCO_2 per minute"),
       #title = "Relative contribution of variance over age",
       colour =  "Treatment") + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none",
        strip.text = element_text(size = 18),
        strip.background = element_blank())
```

```{r, eval = TRUE, cache = TRUE}
#Read in model
mod.imp.3.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/mod.imp.3")

#Make a figure from model predictions using mod.imp.3.obj
mod.3.imp.post <- posterior_samples(mod.imp.3.obj) 
names(mod.3.imp.post)[1:14]
names(mod.3.imp.post)[120:150]

#Specificying the posterior
post = mod.3.imp.post

#Try pmap
imp_model_predictions <- bind_rows(pmap(new_data, imp_mr_pred))
str(imp_model_predictions)
rownames(imp_model_predictions) <- NULL

#Check it
imp_model_predictions %>% filter(id == "ld0449" & samp_session == 1) #Fantastic
model_predictions %>% filter(id == "ld0449" & samp_session == 1)
```

```{r, eval = TRUE, include = TRUE, fig.height = 6.7, fig.width = 9.5}
#Filter out the subset IDS
imp_model_predictions %>% filter(id %in% c(subset_cold, subset_hot) & samp_session %in% c(1,5,10)) %>% 
  ggplot(aes(x = temp, y = mean_lnmr)) + 
  geom_line(aes(group = id, colour = factor(treatment)), stat="smooth", method = "lm", lwd = 0.5, alpha = 0.5) + 
  geom_line(aes(group = factor(treatment), colour = factor(treatment)), stat="smooth", method = "lm", lwd = 2, alpha = 1, position=position_dodge(width = 0.3)) +
  geom_point(alpha = 0.2) + 
  facet_wrap(~samp_session) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) + 
  scale_x_continuous(breaks = c(seq(24,34, by = 2))) + 
  labs(x = "Temperature",
       y = TeX("log VCO_2 per minute"),
       #title = "Relative contribution of variance over age",
       colour =  "Treatment") + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none",
        strip.text = element_text(size = 18),
        strip.background = element_blank())
```

```{r, eval = TRUE}
#Treatment differences in temperature specific repeatabilty
# Read in models
cc_cold.2.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/cc_cold.2.obj")
cc_hot.2.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/cc_hot.2.obj")

#Poster names
names(posterior_samples(cc_cold.2.obj))[1:10]

#Temp define:
temp <- seq(24,34, by = 2)
#map(new_data %>% select(temp) %>% distinct(), brms_rpt) #Can't get this to work

cold_rpt <- bind_rows(lapply(temp, function(x) brms_rpt(x, model = cc_cold.2.obj)))
cold_rpt %<>%  mutate(treatment = "cold")

hot_rpt <- bind_rows(lapply(temp, function(x) brms_rpt(x, model = cc_hot.2.obj)))
hot_rpt %<>%  mutate(treatment = "hot")

rpt_data <- bind_rows(cold_rpt, hot_rpt)
```

```{r, eval = TRUE, include = TRUE, fig.height = 6.7, fig.width = 9.5, cache = TRUE}
#plot this
ggplot(rpt_data, aes(x = factor(temp), y = rpt, group = treatment, colour = treatment)) + 
  geom_point(position = position_dodge(0.5), size = 4) + 
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0, position = position_dodge(0.5), size = 0.6) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) +
  ylim(c(0, 0.4)) + 
  labs(x = "Temperature",
       y = "Repeatability",
       colour =  "Treatment") + 
  theme_bw() +
  my_theme + 
  theme(legend.position = "none") 
```

## How does developmental temperature affect temperature specific repeatability

Lizards born in cold developmental temperatures had on higher repeatabilty compared to lizards from the hot developmental temeprature however, credible intervals overlap partially (Fig. XX, Table XX). Across both treatment grounts, repeatability did not change across acute temperatures (Fig.2, Table XX).  
