---
title: "Population and Parental effects"
author: "Fonti Kar"
date: "30/09/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE,
                      echo = FALSE, 
                      include = FALSE, 
                      warning = FALSE,
                      message = FALSE)
rm(list=ls())
sessionInfo()

pacman::p_load(dplyr, magrittr, ggplot2, purrr, Rphylopars, phytools, GGally, mice, janitor, patchwork, GGally, psych, brms, mi, pander,latex2exp, stringr, tidybayes, bayestestR)
```

# Read in data

```{r}
#Metab data
CC_data <-read.csv("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/data/processed/CC_Long_Tinc_MR.csv", stringsAsFactors = F)

mi_data <- read.csv("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/data/processed/Long_Tinc_MR_MI.csv", stringsAsFactors = F)

#Parents
parentage <- read.csv("~/Dropbox/1 - PhD/4 - ldeli_growthrate/data/SNP/Wide_Parentage_ID_assigned.csv", stringsAsFactors = F)

#Population
adults_pop <- read.csv("~/Dropbox/1 - PhD/4 - ldeli_growthrate/data/egg_lizard/adult_data.csv", stringsAsFactors = F)
```

L. 127: Are the three females all coming from the same location? I think this question comes with the (only) real concern I have with this study: could the habitat of origin biased your results via local adaptation of the plastic response? Could this be accounted for in your analyses?

## First we need to assign parents to populations

```{r}
#Need to merge parents data with population data
names(parentage)
names(adults_pop)

#Before we do that we need to change the var names
adults_pop %<>% rename(f0_id = liz_id,
                       sex = liz_sex,
                       population = liz_collect_site)

#Merge population to parentage
head(parentage)
parentage %>% arrange(Dam) %>% tibble()
Mum <- parentage %>% rename(f0_id = Dam)
Dad <- parentage %>% rename(f0_id = Sire)

#Merging by Dam and Sire seperately
pop_mum <- left_join(Mum, adults_pop %>% select(f0_id, population), by = "f0_id")
pop_mum %<>% rename(dam_population = population)

pop_dad <- left_join(Dad, adults_pop %>% select(f0_id, population), by = "f0_id")
pop_dad %<>% rename(sire_population = population)

#Combining and creating a factorial for mum and dad pop id
new_parentage <- bind_cols(pop_mum, pop_dad$sire_population)
new_parentage %<>% rename(Dam = f0_id,
                          sire_population = ...9)

#Clean up blank cells
new_parentage %<>% mutate(sire_population = ifelse( is.na(sire_population) | sire_population == "", NA, sire_population) )

new_parentage %<>% mutate(parent_pop = ifelse(is.na(sire_population), dam_population,
                                             paste0(dam_population, "_" , sire_population)))
#Rename F1_LD_ID to id
new_parentage %<>% rename(id = F1_LD_ID)
```

## First we need to figure out who are the parents

```{r}
#Need baby ids first
baby_data <- mi_data %>% select(id, treatment) %>% distinct %>% tibble()

#Merge:
baby_data <- left_join(baby_data, new_parentage %>% select(id, Dam, Sire, dam_population:parent_pop), by = "id")
baby_data %>% filter(is.na(Dam) | is.na(Sire)) #Okay 2 babies one from each treatment we can't assign thats all good, exclude thems
```

## Now merge into the datasets just do with mi and cc and create z_temp

```{r}
# Mi data
rev_mi_data <- left_join(mi_data, baby_data)
rev_mi_data %<>% mutate(z_temp = scale(temp)[,1])
write.csv(rev_mi_data, "~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/data/processed/revision_mi.csv")

# Complete
rev_cc_data <-left_join(CC_data, baby_data)
rev_cc_data %<>% mutate(z_temp = scale(temp)[,1])

write.csv(rev_cc_data, "~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/data/processed/revision_complete.csv")
```

## Now what are the models we need to rerun?

### Complete case

```{r}
cc_mod.rev.1 <- brm(lnmr ~ treatment*z_temp + z_lnmass + z_age 
                    + (1 + z_temp | id) + (1 | samp_session) + (1 | series_temp) 
                    + (1 | Dam) + (1 | Sire),
                    data = rev_cc_data, 
                    chains = 2, cores = 1, iter = 2000, warmup = 500, thin = 5,
                    control = list(adapt_delta = 0.99, 
                                   max_treedepth = 15))

summary(cc_mod.rev.1)

cc_mod.rev.2 <- brm(lnmr ~ treatment*z_temp + z_lnmass + z_age 
                    + (1 + z_temp | id) + (1 | samp_session) + (1 | series_temp) 
                    + (1 | Dam) + (1 | Sire) + (1 | parent_pop),
                    data = rev_cc_data, 
                    chains = 4, cores = 1, iter = 4000, warmup = 1500, thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 15))



cc_mod.rev.3 <- brm(lnmr ~ treatment*z_temp + z_lnmass + z_age 
                    + (1 + z_temp | id) + (1 | samp_session) + (1 | series_temp) 
                    + (1 | Dam) + (1 | Sire) + (1 | dam_population),
                    data = rev_cc_data, 
                    chains = 4, cores = 1, iter = 4000, warmup = 1500, thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 15))

cc_mod.rev.4 <- brm(lnmr ~ treatment*z_temp + z_lnmass + z_age 
                    + (1 + z_temp | id) + (1 | samp_session) + (1 | series_temp) 
                    + (1 | Dam),
                    data = rev_cc_data, 
                    chains = 4, cores = 1, iter = 4000, warmup = 1500, thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 15))

cc_mod.rev.5 <- brm(lnmr ~ treatment*z_temp + z_lnmass + z_age 
                    + (1 + z_temp | id) + (1 | samp_session) + (1 | series_temp) 
                    + (1 | parent_pop),
                    data = rev_cc_data, 
                    chains = 4, cores = 1, iter = 4000, warmup = 1500, thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 15))
```

### Unpack

```{r}
#I want to compare it againest the og model
cc_mod.3.obj <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/cc_mod.z3.obj")

cc_mod.rev.1 <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/rev/cc_mod.rev.1")
summary(cc_mod.rev.1)

cc_mod.rev.2 <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/rev/cc_mod.rev.2")
summary(cc_mod.rev.2)

cc_mod.rev.3 <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/rev/cc_mod.rev.3")
summary(cc_mod.rev.3)

cc_mod.rev.4 <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/rev/cc_mod.rev.4")
summary(cc_mod.rev.4)

cc_mod.rev.5 <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/rev/cc_mod.rev.5")
summary(cc_mod.rev.5)

cc_mod.rev.6 <- readRDS("~/Dropbox/1 - PhD/5 - Ldeli_inc_metabTelo/output/rds/rev/cc_mod.rev.6")
summary(cc_mod.rev.6)
```

## Information criterions

```{r}

#Add waics
ccr_waic.0 <- waic(cc_mod.3.obj)
ccr_waic.1 <- waic(cc_mod.rev.1)
ccr_waic.2 <- waic(cc_mod.rev.2)
ccr_waic.3 <- waic(cc_mod.rev.3)
ccr_waic.4 <- waic(cc_mod.rev.4)
ccr_waic.5 <- waic(cc_mod.rev.5)
ccr_waic.6 <- waic(cc_mod.rev.6)

loo_compare(ccr_waic.0,
            ccr_waic.1)

wAIC_comp <- loo_compare(ccr_waic.1,
                         ccr_waic.2,
                         ccr_waic.3,
                         ccr_waic.4,
                         ccr_waic.5,
                         ccr_waic.6)

wAIC_comp <- wAIC_comp[,c(7, 1:2)]
wAIC_comp

#              elpd_diff se_diff
# cc_mod.rev.2  0.0       0.0   
# cc_mod.rev.4 -0.6       2.2   
# cc_mod.rev.3 -1.8       2.3   
# cc_mod.rev.6 -3.3       2.2   
# cc_mod.rev.5 -3.7       2.1   
# cc_mod.rev.1 -4.5       3.0 

#Tabulate this: 
as.data.frame(wAIC_comp) %>% write.csv("output/tab/rev/WAIC_comp.csv")




# ccr_loo.0 <- add_criterion(cc_mod.3.obj, "loo")
# ccr_loo.1 <- add_criterion(cc_mod.rev.1, "loo")
# ccr_loo.2 <- add_criterion(cc_mod.rev.2, "loo")
# ccr_loo.3 <- add_criterion(cc_mod.rev.3, "loo")
# ccr_loo.4 <- add_criterion(cc_mod.rev.4, "loo")
# ccr_loo.5 <- add_criterion(cc_mod.rev.5, "loo")
# ccr_loo.6 <- add_criterion(cc_mod.rev.6, "loo")
# 
# loo(ccr_loo.1,
#     ccr_loo.2,
#     ccr_loo.3,
#     ccr_loo.4,
#     ccr_loo.5,
#     ccr_loo.6)

```



